%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

\documentclass[a4paper,10pt,twocolumn]{article}

% \usepackage{multicol}          %multicols or multicol?

% Page Layout
% See: http://amath.colorado.edu/documentation/LaTeX/reference/layout.html

% @TODO: Use \url instead of \href when no text is available.

% multicolumn becomes more readable with smaller margins
\usepackage[cm]{fullpage}       %set all margins to be 1cm
% \addtolength{\textwidth}{5cm}
% \addtolength{\hoffset}{-2.5cm}
% \addtolength{\textheight}{5cm}
% \addtolength{\voffset}{-2.5cm}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{keystroke}
\usepackage{hyperref}
\usepackage{underscore}

% Listings ====================================================================
\usepackage{listings}           %for code listings
\newcommand{\codeC}[1]{\lstset{language=C}\lstinline!#1!}
\newcommand{\codeCVar}[1]{\lstset{language=C}\lstinline!#1!}
\newcommand{\codeCFun}[1]{\lstset{language=C}\lstinline!#1!}
\newcommand{\codeCxx}[1]{\lstset{language=C++}\lstinline!#1!}
\newcommand{\codeCxxClass}[1]{\lstset{language=C++}\lstinline!#1!}
\newcommand{\codeREL}[1]{\lstset{language=C++}\lstinline!REL_#1!}
\newcommand{\codeHaskell}[1]{\lstset{language=Haskell}\lstinline!#1!}
\lstset{
  frame=tb,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=true,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle={\bf\color{Purple1}},
  commentstyle={\it\color{Firebrick4}},
  stringstyle=\color{VioletRed4},
  frame=single,
  breaklines=true,
  breakatwhitespace=true
  tabsize=8
}

% New Commands
% Wikimedia is the default argument
\newcommand{\testcmd}[2][Wikimedia]{This is the Wikibook about LaTeX supported by {#1} and {#2}!}

\newcommand{\hrefn}[2]{\href{#1}{#2}\footnote{See {\texttt #1}}} %HyperRef and Footnote in one

\newcommand{\sn}[0]{SemNet}

\title{\texttt{semnet} --- A Semantic Network Pattern Matching Engine}
\author{Per Nordlöw}
\date{\today}

\begin{document}

\maketitle

% \begin{multicols}{2}

\tableofcontents

\section{What is SemNet?}
\sn{} is a new kind of \emph{pattern matching} engine tightly coupled to the
file system. It's designed to index large amounts of \emph{graph}-linked data
structures. The bidirectional graph is the most general data structure which
naturally emerges in many kinds of data today, typically in source code
structures, thereby \emph{superseding} the traditional hierarchical structure
used in most traditional file systems.

\subsection{Brain-like}

The basic assumption behind the \emph{infrastructure} of \sn{} is that,

\begin{quotation}
  like the \emph{massively interconnected human brain}, the key to
  \emph{efficient} and \emph{usable} storage lies in number of relations
  (associations) that can be defined between \emph{fine-grained} patterns.
\end{quotation}

Therefore \sn{} expresses as much knowledge as possible through semanticly
typed (\codeREL{t}) relations between \codeCxx{Ob} entries in
\codeCxx{Reg}. See \hrefn{http://en.wikipedia.org/wiki/Typed_link}{Typed link}.

Another consequence of this \texttt{{}"{}}\emph{prepare for the
  future}\texttt{{}"{}}-assumption is that \emph{random access time} of any part
of the content is within the same order of magnitude. This is motivated by the
current explosion of \emph{solid-state drives} (SSD) as replacements for hard
disks. Access times and lookups of relations are 100 to 1000 times faster than
hard disks. This in turn motivates the use of random accesses in search and
match algorithms and structuring data in graphs instead of tables.

\section{Patterns}

% \section{Pattern Language}

% Syntax is C-like to make it popular for developers (compare with
% \hrefn{http://www.hyperrealm.com/libconfig/}{libconfig}).

\sn{} is \emph{data-driven} by \emph{graphs} of \emph{pattern specifications}
(\codeCxxClass{Patt}). This contrasts most other \emph{code-driven} software.

\subsection{Data-Driven}
A data-driven architecture enables
\begin{itemize}
\item \emph{self-reflection} of properties such as \emph{size range and
    complexity} of instances (samples),
\item \emph{approximate} matching by relaxing sub-conditions such situation
  (\codeCxxClass{Sit}) and context (\codeCxxClass{Ctx}),
\item \emph{flexible pattern specifications} not bound specifically to file
  streams but can instead operate on \emph{raw devices} for example when
  \emph{rescuing crashed file systems} and
\item easier integration with \emph{code-generation} applications such as in
  evolutionary computations (EC).
\end{itemize}

\subsection{Graph-Structured}
A graph-structured pattern representation enables
\begin{itemize}
\item better \emph{reuse} of sub-patterns, for example across different language
  parsers.
\end{itemize}

\subsection{Fine-Grained}

All patterns are broken down into \emph{sub-patterns} and eventually to
\emph{atomic} patterns (\emph{constant literals}). This improves flexibility and
a higher degree of pattern \emph{reuse} possible. It also unifies descriptions of
\emph{lexical} and \emph{semantic} patterns into one common, often directed, graph.

\section{Text}

In textual processing \emph{lexical}, \emph{syntactic} and \emph{semantic}
building blocks of text (generalizing the concept of \emph{pre-compiled
  headers}, PCH, in compilers).

\section{Matching}

\section{Caching}

\subsection{Memoized Intermediates}
Most scan hits and operation outputs (final and intermediate) are automatically
\emph{persistently} (written on disk) \emph{cached} (\emph{memoized}) if they
are \emph{sufficiently small} compared to the input size. See \codeREL{OP_CACHE}
and \codeREL{CACHING_OP}.

\subsection{Numerical}

Sampled numerical arrays of data could cache, for example, \emph{sum} (and in
turn mean/average), \emph{product} (and in turn \emph{geometric average}) and
\emph{unnormalized moment} (variance, skew, kurtosis).

\subsection{INO-Hashing}

The output hash key is either an integer code (pre-defined or dynamic) or a
serialization (or \emph{check sum} hash) of the \emph{network} that produced the
intermediate result. This output hash is in turn stored in hash-table using the
input data as the hash-key. I will call this hashing INO-Hashing, short for
Input-plus-Network to Output Hashing.

\subsubsection{Hash Chains}
\hrefn{http://en.wikipedia.org/wiki/Hash_chain}{Hash-chains} (hashes of hashes)
are used to calculate INO-hashes of (\emph{hierarchical}) computational networks
containing sub-networks (\emph{modules}). This is similar to how the version
control system Git
\hrefn{http://www-cs-students.stanford.edu/\~{}blynn/gitmagic/index.html}{assures}
data integrity on its history.

\subsubsection{Fitness}

Specifically in Evolutionary Computation (EC) we avoid the cost of evaluating a
specific network more than once through a \emph{fitness cache} using a hash (say
SHA-1) of the input and the network's cellular code.

\section{\emph{Self-Reflective} Patterns}

\sn{} patterns are represented in an \emph{object-oriented},
\emph{graph-structured}, \emph{reusable} and \emph{fine-grained} format. This
enables us to write algorithms that can \emph{analyze}, in statistical way, what
the patterns describe and therefore realize \emph{global pattern matching}. It
also enables \textbf{auto-generation} of pattern \textbf{instances}. To make
this interactable we then describe these patterns in a truly \emph{graphical
  language} supported by \textbf{DVis}. This language can then be used to
describe a pattern matching, for example, {\centering \emph{some
    \textbf{directory} containing some \textbf{file} having some kind of
    \textbf{attribute} and some kind of \textbf{content}.}  }  If we also need
optimal performance we can supplement the matcher with a hand-written
specialized function that performs the same matching.

\section{Real-Time Synchronized}

No more rescanning and parsing.

Detects \emph{external changes} from either
\begin{description}
\item[inotify] detectes file changes
\item[fanotify] provides \emph{on access file scanning} requested by
  anti-malware vendors.
\item[\hrefn{http://stefan.buettcher.org/cs/fschange/index.html}{fschange}]
\item[\hrefn{http://freshmeat.net/projects/rfsdelta/}{rfsdelta}]
\end{description}
and tags all content as obseleted (using \codeC{Ob::obs_flag}) (and when
needed) distribute these tags to relating objects.

Inotify and fanotify of these relies on the \emph{fsnotify} in kernel
infrastructure.

Reorder idle processing queue according to distance to current user interaction
context such as the \emph{current directory} of (shell) process. Use for example
in cases where sound/picture/ and movie concat based on their beginnings ends.

\section{Information Types}

Stores and Processes all kinds of information (including real-life \emph{analog} data):
\begin{itemize}
\item Audio/Sound
\item Images/Pictures
\item Video
\item Human Languages
\item Computer Languages
\end{itemize}

\section{Unification}

\emph{Unification} of Search and Replace Tools, IDEs, Editors, Tag/Intellisense
Databases, VCS, Refactoring, Compilers, Linkers, Unit Testers, Interpreters,
Shells.

\section{Wishlist}

\begin{itemize}
\item \textbf{Search and Replace}: Only operates on special kinds of
  information. For example one function for search and renaming files and
  another for replacing words in files. Is is important that search and replace
  is \emph{interactive} and generates the hits \emph{dynamically} so that the
  user can interact with the first element of the resulting set of hits as soon
  it is generated (compare with Emacs' grep and compilation interface).

  Query Replaces should provide the alternatives: \mbox{$[$}y,n,Y,N\mbox{$]$}
  were \mbox{$[$}y,n\mbox{$]$} applies/skips the current replace and
  \mbox{$[$}Y,N\mbox{$]$} applies/skips the replaces for all occurrencies in the
  current file (compare with Emacs \texttt{query-replace.*}()).
\item \emph{Unified Namespace for \textbf{all} Content} reaching all Nodes and
  Paths in Content Graph with \emph{prefix}, \emph{suffix} and \emph{partial}
  completion. Examples:
  \begin{itemize}
  \item \texttt{/etc/passwd\textbf{::}modification_time} (Read-Write in DVis)
  \item \texttt{/etc/passwd\textbf{::}size} (Read-Only in DVis)
  \item \texttt{/etc/passwd\textbf{::}xattr.user.SemNet.chash.SHA1} (Ignored by
    semnet)
  \item
    \texttt{/etc/passwd\textbf{{\char64}}lines\mbox{$[$}1-10\mbox{$]$}\textbf{{\char64}}columns\mbox{$[$}1-3\mbox{$]$}}
    where \textbf{{\char64}} is the \emph{content-addressing} scope operator.
  \end{itemize} It may be more suitable to use a special Unicode symbol, say the
  mathematical \emph{member of}, representing \emph{scope}. Typically inserted
  using \texttt{Ctrl} plus \texttt{DownArrow}.
\item \emph{Generalized Query-and-Operate Language} that uses Unicode Section
  \emph{Mathematical Operators}. No more backquoting of language specialized
  characters is needed. Examples:
  \begin{itemize}
  \item \emph{Update} a set of files from a given source.
  \item \emph{Copy} all files of type \emph{\texttt{{}"{}}C Source
      Code\texttt{{}"{}}} to a given destination.
  \item \emph{Remove} /etc/passwd\textbf{::}line\mbox{$[$}0\mbox{$]$}.
  \end{itemize}
\item \emph{Filesystem-Global Operation Proposal}: Any Content should
  automatically present to the user what can be done with it and vice versa:
  \begin{itemize}
  \item \textbf{Any}: Delete. Deletion should warn if file is
    used (opened) by other process (see source of lsof for details).
  \item \textbf{Autogenerated Content}: \emph{Updated} from source, but
    \emph{not} explicitly edited. Example: Content generated by
    \emph{autotools}. Example: \texttt{Makefile} generated from \texttt{Makefile.am}
    and \texttt{Makefile.in}. Example: \texttt{configure} generated by
    \texttt{autoconf}(\texttt{configure.ac} or \texttt{configure.in})
  \item \textbf{File/Directory}: Copied/Cloned, Copied/Cloned to, Moved To,
    Check references to and from.
  \item \textbf{Version Controlled Directory}: VC Operations. See Emacs VC
    Interface to hints. Extra feature: Finding local matching (cloned)) repositories
    (git, hg, bzr) that can be pulled from each other synchronized. File Patterns:
    (\texttt{.svn}, \texttt{CVS}, \texttt{.git}, \texttt{.bzr}, etc)
  \item \textbf{Text Files}: Edited. File Patterns: \texttt{.txt}
  \item \textbf{Shell Scripts}: Executed. File Patterns: \texttt{.sh},
    etc. Completion of possible customizable variables defined inside
    scripts. Example call: \texttt{call do_something.sh with ARG=val;}
  \item \textbf{Executables and Libraries (Shared and Static) (ELF, COFF)}:
    Queried for Internal Structure (objdump) such as Symbols, Platform, etc using C
    header file \hrefn{file:/usr/include/elf.h}{elf.h} and libelf. Also see
    \hrefn{http://docs.sun.com/app/docs/doc/816-0217/6m6nhta90?a=view}{elf(3ELF)}
  \item \textbf{Makefiles}: Built using (GNU) \texttt{make}. File Patterns:
    \texttt{\mbox{$[$}mM\mbox{$]$}akefile},
    \texttt{GNU\mbox{$[$}mM\mbox{$]$}akefile}
  \item \textbf{Autoconf}: Built using \texttt{autoconf}. File Patterns:
    \texttt{configure.ac},\texttt{configure.in}
  \item \textbf{Packages} File Patterns \texttt{.*/lib/pkgconfig/.*}
  \end{itemize}
\item Is it possible to automatically detect relations between files and the
  programs that operate on then? Ask Google Groups.
\end{itemize}

\section{Applications}

\subsection{In-Symbol Completion Mechanism}

Example: Completing at the letter \texttt{A} in the string \codeCxx{VRELA_NEW}
gives \codeC{VRELAY_NEW}. Compare with Emacs package \texttt{mdabbrev.el}.

Related to this is completion of \emph{Regular Expression}
\texttt{x} when
set of search hits matching \texttt{x} is available.

Completion should work also by \emph{reordering subwords} (delimited by
\texttt{'-'} or \texttt{'_'}):
{\centering             \texttt{bar-foo} is completed/corrected to \texttt{foo-bar}
}          This completion could be implemented using an algorithm found in
Weiss's book (31666-3) (something with least consecutive substring...).

\subsection{New Kinds of Search and Compare/Match Mechanisms}

\begin{itemize}
\item \emph{Clustered Search and Replace} based on search hit \emph{context}.
\item \emph{Fuzzy Search}: In combination with my Fuzzy Search Algorithm
  (length-normalized) matches of sentences with \sn{} provides a new way of
  asking questions to the computer. Enables quick browsing through manual-pages,
  info-pages, html-titles/content, etc.
\item Automatic Expansion of Acronyms and Substitution of Synonyms aswell as
  automatic revertal to these after exact matches are shown.
\item Generic Global (Recursive) Matching
  \begin{itemize}
  \item Matches of Similar Tree Patterns in File Systems Trees (compare with
    version control systems)
  \end{itemize}
\end{itemize}

\subsection{More Clever File System Synchronizations based on \emph{content}.}

With \emph{O(1)} file comparison performance \sn{} can keep track of
directories that partly or completely share the same content.  Perhaps a
\codeCxx{Dir::sub_copy_counter} that counts the number of childs having content copies
is the thing to use.  A suitable relation type could be named
\codeREL{DUPLICATE_CONTENT}.

This enables very clever synchronization mechanisms, that don't require the user
to name directories sharing a similar sub-structure with a common name.  Compare
with \textbf{\hrefn{http://git.or.cz/}{git}}: \emph{a fast content adressable
  file system}.

\subsection{Self-Relating/Attracting Objects}
Auto discover input-code-output relations. Applications: auto-recompile/rebuild
objects from sources code, auto-unit-test, auto-visualize upon file (region
modifications.

\emph{Fuzzy-parsing} is \emph{fault-tolerant} to unmatched braces and
quotes through most \emph{most probable} pattern data match.

Knows which \emph{combination of objects} that can \emph{interact} with each
other. For example \emph{functions} that operate on specific a
\emph{combination} of data types/structures. Useful, for example, in the
programming languages C and C++ for single argument functions, and in all other
languages for multi-argument functions.

\subsection{Duplicate Detection and Operations on these}
\begin{itemize}
\item Convert \emph{duplicates} (\codeREL{COPY}) to \emph{symbolic links.}
  (\codeREL{SOURCE} and (\codeREL{TARGET}) or vice versa.
\end{itemize}

\subsubsection{Delete Content having Duplicate Names and or Content}
Remove elements (downloaded files) in selection (current directory) already
present elsewhere (in other directory or repository).

\subsubsection{Deleted Files}
Remove content from only of several synchronized directories and want the
\emph{deletions} to be \emph{synchronized} aswell.  Use both name- and
content-hashing of files.

\subsection{Completion}

Complete Indexing of all C and C++ header files in system include path, normally
in \texttt{/usr/include} and \texttt{/usr/local/include}.  Enables automatic
insertion of \texttt{\#include} statements.  Example: if not already included
the statement \texttt{\#include \texttt{{}"{}}string.h\texttt{{}"{}}} gets
automatically included when \texttt{strcpy()} is used. Should work for both
local and system includes.

\subsection{Language Translation}

Automatic Translation/Conversion between \emph{GUI} Toolkits: MOTIF,
  WxWidgets, GTK, Qt, Java Swing, etc.

\subsection{More Advanced Syntax Highlighting}

\begin{itemize}
\item Colorize the \emph{use} of \emph{Functions}, \emph{Variables},
  \emph{Constants}, \emph{Types}, \emph{Structures} (Type attributes plus
  boldness), \emph{Classes}, \emph{Function Arguments/Variables},
  \emph{Preprocessor Macros} and \emph{Constants} not only their definitions.
\end{itemize}

\subsection{Reverse Engineering of Data Formats (File Types)}

By training a database with a set of example files for each file format using
template matchings.

\subsection{Reverse Engineering of Computer Languages by \emph{learning} from Example Code}

Syntax of Natural and Computer Languages are automatically learned from working
examples. Pitfalls are learned from incorrect examples.
\begin{itemize}
\item \emph{Keywords}: Occur frequently and are in C/C++/Java/C\# not assigned
  to nor used in any arithmetical or logical expressions.
\end{itemize}

\subsection{Reverse Engineering the Structure (Reverse-Structuring) of Code Projects}

\begin{itemize}
\item Finds Class Inheritance of Object-Oriented Languages.
\item Finds Functional Dependencies.
\end{itemize}

\subsection{Detection of Computer Languages by \emph{testing} Different Matchers,
  Ranking and Comparing the Results}

Examples of Applications: Auto-highlight source-code inside HTML \texttt{pre}
and \texttt{code} tags. Ranking must somehow \emph{promote fewer but more
  complex patterns higher than more but less complex patterns}. One simple
example could be {\centering higher-pattern-rank = 2 * sum-of-its-child-ranks }
or perhaps {\centering higher-pattern-rank = 1 + sum-of-its-child-ranks }

\subsection{Software Metrics and Statistics}

\begin{description}
\item[Frequencies] Number of Min/Max/Mean-Length of
  \begin{itemize}
  \item Functions
  \item Variables
  \item Constants
  \end{itemize}
\item[Code Reuse] Measured as attributes of call-tree.
\item[Code Complexity] See for example McCabe's
  \hrefn{http://en.wikipedia.org/wiki/Cyclomatic\_complexity}{Cyclomatic
    Complexity} Metrics and the commercial software
  \hrefn{http://www.sgvsarc.com/overview\_software.htm}{SGV SARC}.

\item[Syntax Detection] Prerequisites are ASCII categories are
  \begin{itemize} \item Braces: \mbox{$[$}\mbox{$]$}, (), \{\},
    % < href="http://en.wikipedia.org/wiki/Cyclomatic_complexity">
  \item Identifier Parts (english Letters and underscore):
    \mbox{$[$}a-zA-Z\_\mbox{$]$}
  \item Numbers: \mbox{$[$}0-9\mbox{$]$}
  \end{itemize}
\end{description}

\subsection{Code Format Detection}

\begin{itemize}
\item Braces: \mbox{$[$}\mbox{$]$}, (), \{\},
  % < href="http://en.wikipedia.org/wiki/Cyclomatic_complexity">

\item Identifier Parts (english Letters and underscore):
  \mbox{$[$}a-zA-Z\_\mbox{$]$}
\item Numbers: \mbox{$[$}0-9\mbox{$]$}
\end{itemize}

\subsection{Easy Code Analysis, Completion, Assistance and Refactoring}

\begin{itemize}
\item C to C++ Conversion Assistance.
  \begin{itemize}
  \item Detect Preferred Use of \emph{Class Inheritance}. For example \texttt{
      struct \textbf{B} \{ struct \textbf{A} a; int i; \} b; } is converted to
    \texttt{ class \textbf{B} : public \textbf{A}; } \end{itemize}
\item \emph{Generate Function Testers} directly from sources based on what
  arguments a function takes and \emph{visualize output as a function of its
    arguments}.
\item Detect \emph{Mutable} Members (only defined by other members in struct or
  class).
\item Complete \emph{arguments} to \emph{command} line calls (such as
  \textbf{make}) {\centering \texttt{ make BUILD_TYPE=fast } } based on contents
  of their corresponding implicit or explicit in files (such as
  \textbf{Makefile}): {\centering \texttt{ifeq (\$(BUILD_TYPE),fast)} } or
  perhaps even more complete using the regular expression
  \texttt{\mbox{$[$}A-Z_\mbox{$]$}+=}.
\item Easy \emph{Function Extraction/Removal}
\item Easy \emph{Removal}, \emph{Adding} and \emph{Reordering} of Function
  Arguments
\item \emph{Merging} of a Set of Variables {\centering \texttt{ int x, y; } }
  into a C structure or C++ class: {\centering \texttt{ vec2i vi; } } that also
  suggests update of function arguments adjacently containing structure member
  types.
\item \emph{Optimization} of Logic. For example the Lisp expression {\centering
    \texttt{(if x x y)} } is equivalent to the more compact {\centering \texttt{(or
      x y)} } that also suggests update of function arguments adjacently containing
  structure member types.
\item \emph{Detection} of \emph{Initialization-Clearing} Function Pairs like
  \texttt{mpz_init()} and \texttt{mpz_clear()} and possibly automatic conversion
  to C++ Constructors and Destructors.
\item Checking of \emph{Argument Naming} in function declaration and definition.
  When analyzing the following code {\centering \texttt{ int inc1(int x); }
    \texttt{ int inc1(int a) \{ return a+1; \} } } \sn{} should be a able to warn
  that the variable of the function \texttt{inc1} is named differently in
  declaration and definition.
\item Function declaration / definition is not a prototype: {\centering \texttt{
      void foo(); } } should automatically suggest a corrected variant:
  {\centering \texttt{ void foo(void); } }
\item Direct Feedback of Name-Clashes in
  \begin{itemize}
  \item Renaming of symbols or files in code-trees (projects)
  \end{itemize}
\item Changing between pass by \emph{value} and pass by \emph{reference}.
  \begin{itemize}
  \item In C between value and pointer.
  \item In C++ between value, pointer or reference.
  \end{itemize}
\item Handling of \emph{adding} and \emph{removal} of sets of parameters to sets
  of functions beginning at position relative to beginning or end of existing
  parameters.
\item \emph{Generalization} of Structures, Classes and Functions into C++
  Templates or Java Generics.
\item Detect \emph{Mismatch} between C/C++ Header Filenames and
  \emph{\#ifdef-\#define-guards}.
\item Assure that the end (case-insensitive) of the C header file constant used
  by the C/C++ CPP Guard ifndef-define-construct is always uptodate with Header
  Filename. Example: \codeC{\$PWD_FILENAME_H} and \emph{no duplicates} of these
  kinds exist in any of the Project and System Header Files.
\item Pairing (stick together) of
  \begin{itemize}
  \item \emph{variable} and \emph{function} declarations (in header file) and
    definition (in source file)
  \end{itemize} when moving these objects across files.
\item Detect \emph{Duplications}
  \begin{itemize}
  \item \emph{Code} Duplications for primarily
    \begin{itemize}
    \item Preprocessor \#defines,
    \item Static Functions but also
    \item Inline Code
    \end{itemize}
  \item \emph{File} Duplications
  \end{itemize}
\item Suggest Preferred Code Editing Style, such as \emph{indentation} style,
  based on the current contents of the file being edited.
\item Detect Mismatched combination of OpenGL Vertex Arrays Functions like
  {\centering \texttt{glVertexPointer(2, GL_FLOAT, 0, points);} and
    \texttt{glDrawArrays(GL_POLYGON, 0, points_num);} }
\item Detect Potential Memory Allocation Bugs like {\centering \texttt{int * x =
      malloc(3 * sizeof(float));} }
\item Detect \emph{Missing Parenthesis} around C Macro Values; {\centering
    \texttt{\#define Y X+1} which should be \texttt{\#define Y (X+1)} }
\item Detect \emph{Obselete Interfaces}: for example use open(2) instead of
  create(2). Other example: string-to-int() => string-to-number() in Emacs Lisp.
\item Syntax Errors *interactively*
\item Detect \emph{Infinite Loops}
\item Detect \emph{Infinite (Cyclic) Recursions}, etc.
\item Detect \emph{Memory Leaks}
\item Detect Function Callgraphs
\item Detect Lack of Check in calls to that memory allocators such malloc return
  a non-zero (NULL) value.
\item Propose \emph{Constant Attribute} to functions that does \emph{not} change
  the variable.
\item \emph{Semantic Completion} and thereby \emph{Automation} of \emph{User
    Input}, mainly for \emph{programming assistance}. Such as in the following
  case: Reads and writes to the boolean variable \texttt{g_sfxs_uopt} is
  mapped to function calls to \texttt{uopts_enable()},
  \texttt{uopts_disable()} and \texttt{uopts_get()}.

  Needs statistics on cursor movement and file editing history at multiple
  structural levels --- byte (offset), lexical, syntactical, semantical, etc.
\end{itemize}

\subsection{Extraction of Communication Paths in source code }

Finding
communication paths between either processes or functions enables us to find
relations.
Patterns: \texttt{socket() SOCK_STREAM, SOCK_DGRAM, SOCK_RAW, SOCK_SEQPACKET,
  SOCK_RDM, read(), write(), sendto(), recvfrom(), msgQ...()}, ... .

\subsection{Language detection using aspell}

Language detection with aspell
spell-checking enables us to automatically determine the encoding of
text-file. Use it first with the words file. Realized using histograms of pfile
word to languages matches.

Using detected language(s) we can then \emph{split} up combined
words such as \emph{filename} into \emph{file} and \emph{name}
and index these separately. This is the \emph{auto-correction}
humans expect from a search function. Many of Googles Services and
many other web search engines, such as Blocket, does \emph{not}
provide this feature, which can be very frustrating.

\subsection{Spelling Correction}

Spelling Correction of Identifiers by comparing with tags (or other databases)
and symbol tables in object files (ELF) and aspell dictionaries.  For details
see \texttt{elf.h} and \texttt{libelf} and \texttt{elf} manual page.  Also see
\hrefn{http://people.freebsd.org/.jkoshy/download/libelf/article.html}{libelf by
  example}

\subsection{Visualize different behaviours in code trees: such as communication paths through queues, sockets, files, etc...}


\subsection{Predicates about any kind of data format and relation}


\subsection{Automatic detection of code (disassembling) and data in binary files}


\subsection{Tag functionality that replaces tags (etags,Exuberant ctags,GNU GLOBAL)}


\subsection{Automatic Detection of Object Attribute Patterns}

Interactive detection of automations by detection of patterns in the commands given by the user - that is automatic suggests suitable macros. Compare Automator on Mac OS X.
Example Usage: Select all words in italic.

\subsection{A Complete Modelling Hierarchy:}


\subsubsection{Code:}

\begin{enumerate}
\item Kernel
\item Process
\item Function (Call Stack)
\item Library
\end{enumerate}

\subsubsection{Content:}

Use FUSE, GNOME GVFS/Gio to simplify traversing all kinds of content.
\begin{enumerate}
\item Internet
\item Networks
\item Sub-Networks
\item Hosts
\item File Systems
\item Directories
\item File
\item Groups (Doxygen)
\item Lexical, Syntactic and Semantic Structures
\item Tags: Word, Statement: Function Call
\item Sub-Tags (\texttt{foo} and \texttt{bar} is a subtag of \texttt{foo_bar})
\item Atom: Character, Byte
\end{enumerate}

\section{Prime Directives}

To make this possible we need some guiding prime directives given in descending
priority (highest first)

\subsection{Trinity: Data Compression, Signal Detection, Signal-Model Fitting.}

\subsection{Detects both \emph{Digital} (Human and Computer Languages) and
  % <en href="http://people.freebsd.org/\~{}jkoshy/download/libelf/article.html">
  Analog
  % </en href="http://people.freebsd.org/\~{}jkoshy/download/libelf/article.html">
  (Real-World) Patterns.}

\subsection{Incremental/Iterative Processing Of Data - no operations go unused
  in the long run.}

\subsection{More efficient reuse of long-time pattern matchings than in
  traditional relational databases.}

\subsection{Minimize Memory Usage}

Highest priority is always to minimize the the memory footprint of knowledge as
I believe this is the fundamental property of a pattern matching intelligence.

\subsection{Reduce Information - a compact and general representation.}

\subsection{Relations}

Design Relations - can be ambiguious, that is N-to-N. And always
*bidirectional*. Are allowed to be UNRESOLVED.

\subsection{Evolve Relations}

\subsection{Find Deviations}

\subsection{Fuzzy Version Number Sort}

Sorting of fuzzy version numbering methods a la x.x.x and filenames ordered
according to numbers: f0, f1.f2 should come prior to f01 f10, f10, f11 osv. It
all depends on the \emph{context}.  All forms of data content is indexed with a
data format specifier DFMT_t currently defined in
\\~{}{}/cognia/tests/t_dvis.c.  We need a very efficient mechanism to describe
WHICH VF_Xi HOW and TO WHAT RELATE to other VF_Y. These relations are be
similar to regular expression operators. The relations should be named something
like: FOP_ANY(), FOP_ALL(), FOP_ALT(), FOP_CAT(), An example of such a
relation may be a function call like: VF_FUNCALL: VF_CAT(VF_IDENT, VF_LPAR,
VF_RPAR): foo() All this information is stored as the most general tree
possible. Relations (between nodes in this tree) also contain a strength value
that is adjusted according to training data.

\section{Language}

Database written in a relational language inspired by Prolog.  \emph{It enforces
  the programmer to reuse intermediate patterns}.  Intermediate patterns are
however also generated in database evolvings through iterations/optimizations.

\section{Simple Syntax}

\# Documentation
IDENT (
% <relation href="http://people.freebsd.org/\~{}jkoshy/download/libelf/article.html">
IDENT+)+

\section{Raw Patterns (Literals)}

The \emph{raw} patterns (\codeCxxClass{Patt}) are separated from their
\emph{meaning}.

\section{Interpretations \& Meaning (\texttt{PINTR_t})}

\subsection{Bit/Byte (Binary) Format}

\begin{itemize}
\item \texttt{UI8}, \texttt{SI8}
\item \texttt{UI16}, \texttt{SI16}
\item \texttt{UI32}, \texttt{SI32}
\item \texttt{UI64}, \texttt{SI64}
\item \texttt{UIxx}, \texttt{SIxx}
\item \texttt{FLOAT}, \texttt{DOUBLE}, \texttt{LONG_DOUBLE}
\item \texttt{COMPLEX}
\end{itemize}

\subsection{Physical Units}

Numerical data can be related to to a \emph{physical} (\emph{singleton})
\codeCxxClass{Unit} object, through which we can reach, for example, all data of a
specific physical unit, which can in turn be used in DVis completion of for
example, adding of numerical entities.

Uses \hrefn{http://marinemetadata.org/news/udunits2}{\texttt{udunits2}}.

\section{Matchers, Hits and Scans}

A \codeCxxClass{Matcher} describes a pattern and its \emph{behaviour} semantics,
syntax and context. A \texttt{patterns::Hit} is an instance of a \codeCxxClass{Matcher}. A
\codeCxxClass{Iter} searches for occurrencies of \codeCxxClass{Matcher}s in a set of
objects and returns \emph{patterns::Hit}s.

\subsection{Matcher}

A matcher falls into one of the following classes:n

\subsubsection{Literal (Terminal, Atom)}

\begin{itemize}
\item atom\textbf{N}: \textbf{N}-bit literal
\item str: string literal (set of ASCII-characters)
\end{itemize}

\subsubsection{Alteration (Regexp): \textit{alt(a,b)} matches \textit{a}
  \emph{or} \textit{b}.}

\subsubsection{Grouping (Regexp): \textit{adj(a,b)}
  matches \textit{a} \emph{adjacently followed by} \textit{b}.}

\subsubsection{Quantification (Repetition) (Regexp): \textit{rep(a,m,n)}
  matches \textit{a} \textit{m} to \textit{n} times.}

\subsubsection{Generic Template (not possible with Regexps)}

We need some way of compactly expressing generic parameter patterns (templates)
Examples:
\begin{itemize}
\item x = x;
\item y = y;
\item z = z;
\end{itemize}
should be automatically detected and stored in database as instantiations of a
template id.

\subsection{Hit}

A hit belongs to one of the following classes:
\begin{itemize}
\item \textbf{patterns::Hit_Const} (phitfc): (Fixed-length) Constant Hit
\item \textbf{patterns::Hit_Fix_RangeL} phit_fix_rl: Fixed-length Upper Limit Hit
\item \textbf{patterns::Hit_Fix_RangeU} phit_fix_ru: Fixed-length Low-Range Hit
\item \textbf{patterns::Hit_Fix} phit_fix: Fixed-length Hit
\item \textbf{patterns::Hit_Var} phit_var: Variable-length Hit
\item \textbf{patterns::Hit_Rep_Adj} phit_rep: Adjacent Repetition
\item \textbf{patterns::Hit_Rep_Ival} phit_rep: Interval Repetition Context...
\end{itemize}

\subsection{Scan}

Scans are \emph{block-coordinated} on memory files to make optimal use of
locality and thereby maximum disk read performance.

\section{Relation types}

Extends single-directional relations for regular expressions to be
bi-directional. See \codeREL{t} in \codeC{SemNet.hpp} for details.

\section{Internal Structure}

\subsubsection{Batch-Oriented Loop:}

\begin{itemize}
\item Update semnet structure.
\end{itemize}
Maximizes the number of relations between all parts down to the smallest parts
of the data, similar to the approach taken by
\hrefn{http://www.namesys.com/v4/v4.html}{Reiser4}.  Assumes \emph{Brain Like
  three-dimensional Processing Structure}. As of 2007 not yet available but will
soon be.

Dynamically built indexed relational \emph{cross-level pattern matching}
database of all sorts of files and their content in the filesystem, such as C /
C++ indentifiers, text-file words etc.

The internal structure for storing patterns and especially templates is crucial
to the performance of \sn{}: {\centering \emph{Postfix or Prefix?}}

Every pattern has a level used in the iteration completion checking.

Specific interpretation of very simple patterns are often highly dependent on
the \emph{context}.

New information is stored through template-matching with previously stored
data. The driving forces here is to
\begin{itemize}
\item minimize the increase of the size of the information (\textit{D_i}) at
  each step. \textit{D_i} can of course be negative in some fortunate
  generalizing cases.
\item reuse computations using information in hierarchical template patterns
\end{itemize}

\subsection{ \emph{Multithreaded} Architecture:}

\codeCxxClass{File}s can be locked and \codeCxxClass{Dir}s can be locked recursively by
analyzing threads.

\subsection{ Content-Based Addressing (CBA) }

\subsection{ Performance Decisions}

Performance order if Importance
\begin{itemize}
\item \textit{Search} (Compare) (\textbf{high} prio)
\item \textit{Add} (Modify) (\textbf{medium} prio)
\item \textit{Remove} (\textbf{low} prio)
\end{itemize}

\subsection{Expand-Reduce Dynamics}

The internal structure is like a parse-tree but generalized to a \emph{network}
of nodes.  Each node is \emph{self-aware} of how it can, possibly recursively,
\emph{expand} its structure to \emph{sub}-structures or together with other
nodes \emph{reduce} its structure to a \emph{super}-structure.

\section{Links and Inspirations}

\begin{itemize}
\item \hrefn{http://en.wikipedia.org/wiki/Semantic_networks/}{Semantic network
    on Wikipedia}
\item
  \hrefn{http://video.google.com/videoplay?docid=2159021324062223592\#}{Everything
    is Miscellaneous} --- how digital information makes us organize things in a
  non-hierarchical \emph{more humane} way, similar to how our brain structures
  information.
\item The Arts, Media and Engineering Library Assortment
  (\hrefn{http://ame4.hc.asu.edu/amelia/}{AMELiA})
\item An Exploration of Object Oriented Database Management Systems
  (\hrefn{http://www.25hoursaday.com/WhyArentYouUsingAnOODBMS.html}{OODBMS})
\item \hrefn{http://www.linux-mag.com/id/7308/}{Linux Don't Need No Stinkin'
    ZFS: BTRFS Intro \& Benchmarks}
\item \hrefn{http://fuse.sourceforge.net/}{FUSE - Filesystem in Userspace}
\item \hrefn{http://en.wikipedia.org/wiki/Filesystem.in.Userspace}{FUSE -
    Filesystem in Userspace on Wikipedia}
\item \hrefn{http://curlftpfs.sourceforge.net/}{CurlFtpFS - A FTP filesystem based on cURL and FUSE}
\item \hrefn{http://lfs.irisa.fr/}{LFS} --- Logical Information Systems
\item \hrefn{http://www.neuroblast.net/}{Evolutionary Intelligence}
\item \hrefn{http://llvm.org/}{The LLVM Compiler Infrastructure}
\item \hrefn{http://research.att.com/.marioh/spatialindex/}{Spatial Index Library}
\item \hrefn{http://www.cs.berkeley.edu/.smcpeak/elkhound/}{Elkhound}: A GLR
  Parser Generator and Elsa: An Elkhound-based C++ Parser
\item \hrefn{http://www.cs.ucr.edu/.stelo/pattern.html}{Pattern Matching Pointers}
\item \hrefn{http://www.program-transformation.org/Transform/WebHome}{Program-Transformation.Org}
\item \hrefn{http://www.ipd.bth.se/ska/sim.home/libghthash.html}{libghthash}
\item \hrefn{http://mhash.sourceforge.net/}{libmhash}
\item \hrefn{http://en.wikipedia.org/wiki/Inotify}{inotify}
\item \hrefn{http://en.wikipedia.org/wiki/Extended.file.attributes}{Extended attributes (\texttt{xattr.h})}
\item \hrefn{http://www.and.org/vstr/comparison}{String library comparison}
\item \hrefn{http://www.cs.sunysb.edu/.algorith/index.html}{The code
    monkey's guide to cryptographic hashes for content-based addressing}
  \hrefn{http://www.linuxworld.com/cgi-bin/mailto/x.linux.cgi?pagetosend=/export/home/httpd/linuxworld/news/2007/111207-hash.html}{hash}
\item \hrefn{http://web.media.mit.edu/.push/why-ai-failed.html}{Why AI Failed -- The Past 10 Years}
\item \hrefn{http://books.google.se/books?id=DWZc9Ti.vBwC.pg=PA339.lpg=PA339.dq=syntactic+hashing.source=bl.ots=2R4oZzGX14.sig=6QWVJQIUxcx1XkEh3N0LkCk8yVM.hl=sv.ei=hkuVStvbAYTs-AbntfnyDQ.sa=X.oi=book.result.ct=result.resnum=1\#v=onepage.q=.f=false}{Structural,
    Syntactic, and Statistical Pattern Recognition: Joint IAPR}
\item \hrefn{http://lwn.net/Articles/370717/\#Comments}{LCA: Static analysis with GCC plugins}
\item mozilla Dehydra
\item \hrefn{http://en.wikipedia.org/wiki/Cyc}{C}
\item \hrefn{http://en.wikipedia.org/wiki/Magnet\_URI\_scheme}{Magnet URI scheme}

\end{itemize}

% \end{multicols}

\end{document}
                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                